### 2018-05-16 Sections/economics_of_the_quantum_internet.tex
Quantcoin protocol fig

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantCoin($\hat{U}_\text{comp}$, blockchain, data, reward):
\begin{enumerate}
	\item Alice possesses the raw input $data$, as well as a $reward$ to pay for its processing (in arbitrary units).
	\item Bob possesses the universal quantum computer, which implements $\hat{U}_\text{comp}$.
	\item Alice encrypts her data using either homomorphic encryption, or a blind quantum computing protocol,
		\begin{align}
			encryptedInput = homoEncrypt(data)
		\end{align}
	\item Alice commits the $encryptedInput$ to the public $blockchain$,
	\begin{align}
	blockchain.commit(encryptedInput)	
	\end{align}
	\item Alice pays Bob the $reward$ to process her data,
	\begin{align}
		give(reward, Alice\to Bob)
	\end{align}
	\item Bob processes the $encryptedInput$ on his quantum computer,
	\begin{align}
		encryptedOutput = \hat{U}_\text{comp}(encryptedInput)
	\end{align}
	\item Bob commits the encrypted output data to the public blockchain,
	\begin{align}
	blockchain.commit(encryptedOutput)	
	\end{align}
	\item Alice and Bob execute a verification protocol,
	\begin{align}
	proof = verify(encryptedOutput)	
	\end{align}
	\item The $proof$ is committed to the $blockchain$ (as is every step of the proof if it is an interactive one),
	\begin{align}
		blockchain.commit(proof)
	\end{align}
	\item The $blockchain$ network inspects that the verification is valid.
	\item If valid, the $blockchain$ cryptographically hashes the data and proof, encapsulating it into a QuantCoin\texttrademark\,token, which is given to Bob,
	\begin{align}
		&token = SHA256(encryptedInput + encryptedOutput + proof)\nonumber\\
		&Bob.receive(token)
	\end{align}
\end{enumerate}}}}
\caption{A rough high-level outline for how a quantum computation-backed cryptocurrency might be implemented\footnote{This is merely a highly simplified toy model in which all computations are of equal value. A consumer-ready implementation would have to handle these and other additional implementation details. However, we expect these finer details ought not alter the overall flavour of the protocol.}. We have abstracted away the underlying Blockchain protocol, interfacing with it using a high-level API. We do this since Blockchain technology is highly liable to change substantially in the coming years -- it might even be a natively quantum Blockchain. We similarly call upon verification subroutines using a high-level implementation-dependent API.} \label{alg:quant_coin}
\end{table}

>>>>

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantCoin($\hat{U}_\text{comp}$, blockchain, data, reward):
\begin{enumerate}
	\item Alice possesses the raw input $data$, as well as a $reward$ to pay for its processing (in arbitrary units).
	\item Bob possesses the universal quantum computer, which implements $\hat{U}_\text{comp}$.
	\item Alice encrypts her data using either homomorphic encryption, or a blind quantum computing protocol,
		\begin{align}
			encryptedInput = homoEncrypt(data)
		\end{align}
	\item Alice commits the $encryptedInput$ to the public $blockchain$,
	\begin{align}
	blockchain.commit(encryptedInput)	
	\end{align}
	\item Alice places into escrow Bob's $reward$ for processing her data,
	\begin{align}
		escrow.hold(reward)
	\end{align}
	\item Bob processes the $encryptedInput$ on his quantum computer,
	\begin{align}
		encryptedOutput = \hat{U}_\text{comp}(encryptedInput)
	\end{align}
	\item Bob commits the encrypted output data to the public blockchain,
	\begin{align}
	blockchain.commit(encryptedOutput)	
	\end{align}
	\item Alice and Bob execute a verification protocol,
	\begin{align}
	proof = verify(encryptedOutput)	
	\end{align}
	\item The $proof$ is committed to the $blockchain$ (as is every step of the proof if it is an interactive one),
	\begin{align}
		blockchain.commit(proof)
	\end{align}
	\item The $blockchain$ network inspects that the verification is valid.
	\item If valid, the $blockchain$ cryptographically hashes the data and proof, encapsulating it into a QuantCoin\texttrademark\,token, which is given to Bob,
	\begin{align}
		&token = SHA256(encryptedInput + encryptedOutput + proof)\nonumber\\
		&Bob.receive(token)
	\end{align}
	\item The reward held in escrow is released to Bob,
	\begin{align}
		escrow.release(Bob)
	\end{align}
\end{enumerate}}}}
\caption{Sketch for how a quantum computation-backed cryptocurrency might be implemented\footnote{In this toy model all computations are of equal value. We expect that addressing these finer details ought not alter the overall flavour of the protocol.}. We have abstracted away the underlying Blockchain protocol, interfacing with it using a high-level API, since Blockchain technology is highly liable to evolve. We similarly call upon verification subroutines using a high-level implementation-independent API.} \label{alg:quant_coin}
\end{table}

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{quantcoin_protocol}
\caption{\comment{To do}}\label{fig:quantcoin_protocol}	
\end{figure}
